\section{\large Questions}

\begin{question}
    Mention the three gas laws; its name and its formula.
    (According to Hugo Lacayo and Michele Lau)
\end{question}

\begin{question}
    Mention who and in what year Boyle's law was invented.
    (According to Fernando Ariaca)
\end{question}

\begin{question}
    Mention the types of pneumatic devices.
    (According to Laura Chavarría and Thais Noguera)
\end{question}

\begin{question}
    Mention who and in what year pneumatic devices was invented.
    (According to Laura Chavarría and Thais Noguera)
\end{question}

\begin{question}
    Mention two specific examples of the application of pneumatic devices.
    (According to Sandra Blanco and Amala Castillo)
\end{question}

\begin{question}
    Mention at least three characteristics of solids.
    (According to Leslie Blanco and Gabriela Pérez)
\end{question}

\begin{question}
    Mention at least two specific situations where the characteristics of solids become relevant.
    (According to MingWei Hsu and Denis Navarro)
\end{question}

\begin{question}
    What do you understand by moduli of deformation?
    (According to Moisés Arauz and Isaac Salas)
\end{question}

\begin{question}
    What is acceleration?
    Mention thinkers and scientists who have contributed to this area.
    (According to Victoria Duarte, Ariana Saavedra, Samuel Sandoval and Alejandra Úbeda)
\end{question}

\begin{question}
    Mention a physical law that describes how acceleration behaves.
    (According to Ariana Saavedra and Alejandra Úbeda)
\end{question}

\begin{question}
    Mention applications of how acceleration is present in everyday life.
    (According to Victoria Duarte and Samuel Sandoval)
\end{question}

\begin{question}
    What is horizontal motion?
    Mention an example where horizontal motion can be seen.
    (According to Carlos Arguello, Jonatan Marín, Federico Picado and Andrea Urbina)
\end{question}